Wikipedia Text Mining and Entropy Analysis

### 2019-03-04 wiki_entropy/wiki_clustering.Rmd
working on imputation

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(missMDA)
library(cluster)
library(widyr)
library(lsa)
library(magrittr)
library(broom)
library(here)
library(feather)
library(FactoMineR)

@@

@@

phon_wf <- wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode) %>%
  select(`1A`:`19A`, language)

phon_wf <- phon_wf[rowSums(is.na(phon_wf)) < 15,]
```

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(googlesheets)
library(lingtypology)
library(knitr)
library(missMDA)
library(cluster)
library(widyr)
library(lsa)
library(magrittr)
library(broom)
library(here)
library(feather)
library(FactoMineR)
library(feather)
library(janitor)

@@

wf <- wals.feature(FEATURES) 
fair_wf <- wf[rowSums(!is.na(wf)) > 50,] %>%
  filter(language %in% LANGUAGES) %>%
  select(-wals.code, -latitude, -longitude, -glottocode) %>%
  as_data_frame()

@@

wa <- fair_wf %>% 
  filter(language %in% LANGUAGES) %>%
  select(`1A`:`19A`, language) %>%
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, `1A`:`19A`) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  column_to_rownames("language") %>%
  as.data.frame(stringsAsFactors = TRUE) %>%
  clean_names() %>% 
  lapply(factor) %>%
  lapply(as.numeric) %>%
  lapply(factor) %>%
  as.data.frame() %>% 
  MIMCA(ncp = 4, maxiter = 100000, threshold = 1e-1)

wa <- as.data.frame(wa[[1]][[99]]) 
wa$language <- unique(phon_wf$language)
```
